---
title: "Homework 7"
format: pdf
author: "GONG Kuiyuan"
---
Student ID: 39-246182

Student name: GONG Kuiyuan

Preferred name: Eddie

## Answers:

**Task 1**:
```{r}
library(pacman)
p_load(datasauRus)

library(pacman)
p_load(dplyr)
```

**Task 2**: We could use either `?` or `help()` to access the documentation.
```{r}
?datasaurus_dozen
#help(datasaurus_dozen)
```

**Task 3**: Combining the information from the documentation, we get to know that `datasaurus_dozen` is a data frame that consists of 1846 rows and 3 columns. `dataset` indicates the sources of dataset, where `x` and `y` are values, respectively.
```{r}
names(datasaurus_dozen)
print(datasaurus_dozen)
str(datasaurus_dozen)
#ncol(datasaurus_dozen)
#nrow(datasaurus_dozen)
datasaurus_dozen |>
  distinct(dataset)
```

**Task 4**:
```{r}
library(pacman)
p_load(ggplot2)

ggplot(
  data = datasaurus_dozen,
  aes(x = x, y = y)
  ) +
  geom_point(color = "black", alpha = 0.7
  ) +
  facet_wrap(~ dataset)
```

**Task 5**: 

```{r}
summary_stats <- datasaurus_dozen |>
  group_by(dataset) |>
  summarise(
    mean_x = mean(x),
    mean_y = mean(y),
    sd_x = sd(x),
    sd_y = sd(y),
    correlation = cor(x, y)
  )
print(summary_stats)
```

**Task 6**: The numbers we got after these operations are very similar with each other. They basically share the same mean, standard deviation and correlation. However, those plots from `Task 4` indicate that there may not be any correlation between `x` and `y` in the first place since the shapes of plots could ba a dinosaur or a star.

**Task 7**: I also stored my plot in `p`.

```{r} 
library(pacman)
p_load(palmerpenguins)

names(penguins)
penguins |>
  distinct(species) |>
  print()

penguins_colors <- c("darkorange", "purple", "cyan4")

p <-
  ggplot(
  data = penguins,
  aes(x = flipper_length_mm,
  y = bill_length_mm,
  color = species)
) +
  geom_point() +
  labs(
    x = "Flipper length (mm)",
    y = "Bill length (mm)",
    title = "Flipper and bill length"
  ) +
  facet_wrap(~ species) +
  scale_color_manual(
  values = penguins_colors
  )

print(p)
```

**Task 8**: I choose the `theme_clean()` from `ggthemes` because I feel like it could make the plot much cleaner and easier for us to observe the data pattern.

```{r}
library(pacman)
p_load(ggthemes)

theme_set(theme_clean())
```

**Task 9**:
```{r}
print(p)
```

**Task 10**:

```{r}
p <- p + theme_economist_white()
print(p)
```

**Task 11**:

```{r}
penguins_colors <- c(
  Chinstrap = "purple",
  Adelie = "darkorange",
  Gentoo = "cyan4"
)
```

**Task 12**: Although I changed the order of species together with its color, it doesn't affect the color assigned to each species unless I change the code into `Adelie = purple`. The color assigned to `Adelie` will be purple in this case.
```{r}
p <-
  ggplot(
  data = penguins,
  aes(x = flipper_length_mm,
  y = bill_length_mm,
  color = species)
) +
  geom_point() +
  labs(
    x = "Flipper length (mm)",
    y = "Bill length (mm)",
    title = "Flipper and bill length"
  ) +
  facet_wrap(~ species) +
  scale_color_manual(
  values = penguins_colors
  ) +
  theme_solarized()
print(p)
```

**Task 13**: Now, we can see that the order of the plot is different, which starts with the `Gentoo` instead of the `Adelie`.

```{r}
penguins$species <- factor(penguins$species, levels = c("Gentoo", "Adelie", "Chinstrap"))

p <-
  ggplot(
  data = penguins,
  aes(x = flipper_length_mm,
  y = bill_length_mm,
  color = species)
) +
  geom_point() +
  labs(
    x = "Flipper length (mm)",
    y = "Bill length (mm)",
    title = "Flipper and bill length"
  ) +
  facet_wrap(~ species) +
  scale_color_manual(
  values = penguins_colors
  )
print(p)
```